Contracts for unions and intersections are hard for Nickel

### 2021-05-21 paper.tex
check on unions and inters

On the other hand, in dynamically typed languages, it is customary to directly
store different kinds of data in one variable without further ceremony. The
runtime system needs to attach type tags to values anyway, which can usually be
observed using functions like JavaScript's \verb+typeof+. Using such bare
unions\resolved{If you can observe with typeof, then it's pretty much a tagged
union, though the tag is implicit} has already been an idiom in dynamically
typed language for a long time. Being able to type and handle these unions is an
important aspect of the migration to a gradual type system. Indeed, a lot of
gradually typed languages either existed originally as dynamically typed
language or aim at backward compatibility with a dynamically typed base
language. This is why despite the presence of a static type system, gradually
typed languages tend to favor bare unions types which is the typed counterpart
of this practice (as e.g in TypeScript \cite{TypeScriptUnions}).

@@

Intersections are less prevalent. An intersection is a value that belongs to to
two types at the same time. A simple example is a number literal \nickel{1}
which could be accepted as both an \nickel{Int} and a \nickel{Float} without
having to perform conversions(Figure~\ref{fig:intersection-subytping-ex}). In
this example, the intersection \nickel{Int & Float} can be used as a subtype of
both \nickel{Int} and \nickel{Float}.

@@

\label{fig:intersection-dual}
\begin{lstlisting}[title={Intersection as the dual of unions}]
f : (Num | String) -> Bool
(*@ $\simeq$ @*) f : (Num -> Bool) (*@ $\cup$ @*) (String -> Bool)
\end{lstlisting}

>>>>

On the other hand, in dynamically typed languages, it is customary to directly
store different kinds of data in one variable without further ceremony. The
runtime system needs to attach type tags to values anyway, which can usually be
observed using functions like JavaScript's \verb+typeof+. Using such bare
unions\resolved{If you can observe with typeof, then it's pretty much a tagged
union, though the tag is implicit} has already been an idiom in dynamically
typed language for a long time. Being able to type and handle these unions is an
important aspect of the migration to a gradual type system. Indeed, a lot of
\unsure{This is the first time discussing gradual type systems, maybe it should
be introduced earlier, in particular how they relate to contracts 
(I think is mentioned on the appendix)}
gradually typed languages either existed originally as dynamically typed
language or aim at backward compatibility with a dynamically typed base
language. This is why despite the presence of a static type system, gradually
typed languages tend to favor bare unions types which is the typed counterpart
of this practice (as e.g in TypeScript \cite{TypeScriptUnions}).

@@

Intersections are less prevalent. An intersection is a value that belongs to
two types at the same time. A simple example is a number literal \nickel{1}
which could be accepted as both an \nickel{Int} and a \nickel{Float} without
having to perform conversions (Figure~\ref{fig:intersection-subytping-ex}). In
this example, the intersection \nickel{Int & Float} can be used as a subtype of
both \nickel{Int} and \nickel{Float}.

@@

\label{fig:intersection-dual}
\begin{lstlisting}[title={Intersection as the dual of unions}]
f : (Num | String) -> Bool
(*@ $\simeq$ @*) f : (Num -> Bool) & (String -> Bool)
\end{lstlisting}
